Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-15 WRITEUP/ms.tex
minor fix typo

We then attempt to characterize/constrain the molecular gas kinematics using an
empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rising part of the curve begins to flatten.
We perform non-linear least squares fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on a Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions with standard deviations
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,988\,$\pm$\,618\,\kms,
$R_{t}$\,=\,10.9\,$\pm$\,7.8\,kpc, and $V_0$\,=\,0\,$\pm$\,9\,\kms.
However, since the emission is not resolved along the flat regime
of the rotation curve, the asymptotic velocity
and the ``turnover'' radius are poorly constrained.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and $-$0.400 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam

>>>>

We then attempt to characterize the molecular gas kinematics using an
empirically-motivated disk model \citep[\eg][]{Courteau97a,Puech08a,Miller11a}:
\begin{equation}
V = V_0 + \frac{2}{\pi} V_{a} \arctan(\frac{R}{R_{t}}),
\end{equation}
where $V$ is the observed velocity, $V_0$ is the velocity at dynamical center,
$V_{a}$ is the asymptotic velocity, and $R_{t}$ is the ``turnover''
radius at which the rising part of the curve begins to flatten.
We perform non-linear least squares fitting using an orthogonal distance
regression to find the best-fit parameters,
taking into account the uncertainties in both velocity (channel width) and
distance offset. We also place an upper limit on $R_{t}$\,$<$15 kpc
to keep this parameter physical \citep[\eg][]{Puech08a,Miller11a}.
The parameter uncertainties are inferred based on a Monte Carlo simulation
of 500 iterations, where the input parameters are perturbed
according to random Gaussian distributions with standard deviations
corresponding to their uncertainties.
Using this model, we find $V_{a}$\,=\,988\,$\pm$\,618\,\kms,
$R_{t}$\,=\,10.9\,$\pm$\,7.8\,kpc, and $V_0$\,=\,0\,$\pm$\,9\,\kms.
However, since the emission is not resolved along the flat regime
of the rotation curve, the asymptotic velocity
and the ``turnover'' radius are poorly constrained.
In particular, $V_{a}$ and $R_{t}$ are highly correlated with a
Pearson coefficient $R$\,=\,0.998, and $-$0.400 between $V_{a}$ and $V_0$. % beam smearing --> not resolving velocity info. within the beam
